%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-0.3cm}
\begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}

% %-------------------------------------------------------------------------------
\cvsubsection{Oral presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Victoria-Muñoz, F.}; Menke, J.; Sánchez-Cruz, N.; Koch. O. 2024. Machine Learning based Scoring Functions: Reasonable Decoy Selection for Automated Docking-based model creation. 2nd School of Chemoinformatics in Latin America, Flash talk, Virtual.}

    \cvpub{\textbf{Victoria-Muñoz, F.}; Menke, J.; Sánchez-Cruz, N.; Koch. O. 2024. Machine Learning based Scoring Functions: Reasonable Decoy Selection for Automated Docking-based model creation. 18th German Conference on Cheminformatics (GCC 2024), Bad Soden am Taunus, Germany.}
    
    \cvpub{\textbf{Victoria-Muñoz, F.}; Menke, J.; Sánchez-Cruz, N.; Koch. O. 2024. Beyond the active: Integrating decoys in machine learning models, PADIF case. Oral presentation: ACS Fall 2024, Denver, Colorado.}
    
    \cvpub{Torres-Garcia, A.;, \textbf{Victoria-Muñoz, F.}; Plazas-Gonzales, E.; Sánchez-Cruz, N.; Sierra-Avila, C. 2023. Natural volatile compounds as possible insecticides. ACS Fall 2023, Virtual.}

     \cvpub{\textbf{Victoria-Muñoz, F.}; Sánchez-Cruz, N.; Medina-Franco J.L.; López-Vallejo F. 2021. Key aminoacidic residues for agonist or antagonist activity against PqsR transcriptional factor from \textit{P. aeruginosa}. ACS Spring 2021, Virtual.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Poster Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}    
    \cvpub{\textbf{Victoria-Muñoz, F.}; Menke, J.; Sánchez-Cruz, N.; Koch. O. 2024. Machine learning based scoring functions: Reasonable decoy selection for automated docking-based model creation. 24th European Symposium on Quantitative Structure-Activity Relationship, Barcelona, Spain.}

    \cvpub{\textbf{Victoria-Muñoz, F.}; Menke, J.; Sánchez-Cruz, N.; Koch. O. 2024. Decoy Selection in Bioactivity Classification Models: Exploring Protein-Ligand Interaction Fingerprints with PADIF. 7th RSC-CICAG/RSC-BMCS Artificial Intelligence in Chemistry, Cambridge, United Kingdom}

    \cvpub{\textbf{Victoria-Muñoz, F.}; Sánchez-Cruz, N.; Medina-Franco J.L.; López-Vallejo F. 2020. Cheminformatics analysis on molecular datasets of transcription factors associated with quorum sensing in \textit{Pseudomonas aeruginosa}. EFMC-ISMC and EFMC-YMCS 2020, Virtual.}

    \cvpub{\textbf{Victoria-Muñoz, F.}; López-Vallejo F. 2019. Cheminformatics analysis of agonist and antagonist of the transcriptional regulators of LasR, PqsR and RhlR in \textit{Pseudomonas aeruginosa}. Poster presentation: XXII Latin-American Meeting on Pharmacology, Cali, Colombia.}

    \cvpub{Undergrad, \textbf{Victoria-Muñoz, F.}, Orozco-López F. 2015. Rational design of new Spiro-beta-lactames as potentials inhibitors of Penicillin binding protein 4. XVI National Congress of Students of Pharmaceutical Chemistry, Cartagena, Colombia.}
\end{cvpubs}
